---
title: "p8105_hw1_cy2752"
author: "Congyu Yang"
date: "2024-09-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1
```{r}
data("penguins",package = "palmerpenguins")
```

In the `penguins` dataset, we have `r ncol(penguins)` variables in total (`r ncol(penguins)` columns).\
They are:`species`,`island`,`billing length` in mm,`bill depth` in mm,`flipper length` in mm, `body mass` in g, `sex` and `year`. \
In variable `species`, we have three categories: `Adelie`,`Chinstrap` and `Gentoo`. \
For variable `island`, we also have three categories:`Biscoe`,`Dream` and `Torgersen`.\
This dataset consists of information from `r nrow(penguins)` samples (`r nrow(penguins)` rows).\
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.


```{r}
(flipper_bill_plot = 
  ggplot(data = penguins,
       mapping = aes(x = bill_length_mm,
                     y = flipper_length_mm,
                     colour = species))+
  geom_point())

ggsave("flipper_and_bill_scatterplot.png",plot = flipper_bill_plot)
```

## Problem 2

```{r}
(random_df = tibble(
  ran_numeric = rnorm(10),
  ran_logical = ran_numeric >0,
  ran_chara = c("ab","cd","ef","gh","ij","kl","mn","op","qr","st"),
  ran_factor = factor(c("low","med","high","low","med",
                        "high","med","high","med","high"))
))
(mean_for_numeric = mean(pull(random_df,ran_numeric)))
(mean_for_logical = mean(pull(random_df,ran_logical)))
(mean_for_chara = mean(pull(random_df,ran_chara)))
(mean_for_factor = mean(pull(random_df,ran_factor)))
```
The mean function works for numerical variable and logical vector; but not working for character vector and factor vector.\

```{r eval = FALSE}
(ran_log_numeric = as.numeric(pull(random_df,ran_logical)))
(ran_chara_numeric = as.numeric(pull(random_df,ran_chara)))
(ran_factor_numeric = as.numeric(pull(random_df,ran_factor)))

```
When we apply `as.numeric` to logical, character and factor variables, we can see:\
logical variable becomes 0 and 1(0 representing FALSE and 1 representing TRUE);\
character variable coerced to be NA;\
and factor variable becomes 1,2 and 3, each stands for one level. \
The reason behind this might be: \
for logical variable, the answer can only be `TRUE` or `FALSE`, we can transfer them to be 0 and 1 representing the chance of issue happened. This also explains why we can take mean of logical variable, it is just showing the proportion of True value.\
for character variable, it can be anything: a sentence, a word or even a paragraph, it cannot be directly converted into numerical variable unless it is just number with quotation mark. Accordingly, it explains why we cannot take mean of character variable.\
for factor variable, we can use `as.numeric` to transfer factor variable to numerical variable, because it is actually `1` stands for `level1`, `2` stands for `level2` ... But we cannot take mean of it. Because for here, numerical values are not simply a number, it has its internal meanings, we are just using a simply way to represent factor variable. This explains what happened when we take the mean value. 

