---
title: "p8105_hw1_cy2752"
author: "Congyu Yang"
date: "2024-09-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1
```{r}
data("penguins",package = "palmerpenguins")
```

In the `penguins` dataset, we have `r ncol(penguins)` variables in total (`r ncol(penguins)` columns).\
They are:`species`,`island`,`billing length` in mm,`bill depth` in mm,`flipper length` in mm, `body mass` in g, `sex` and `year`. \
In variable `species`, we have three categories: `Adelie`,`Chinstrap` and `Gentoo`. \
For variable `island`, we also have three categories:`Biscoe`,`Dream` and `Torgersen`.\
This dataset consists of information from `r nrow(penguins)` samples (`r nrow(penguins)` rows).\
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.


```{r}
(flipper_bill_plot = 
  ggplot(data = penguins,
       mapping = aes(x = bill_length_mm,
                     y = flipper_length_mm,
                     colour = species))+
  geom_point())

ggsave("flipper_and_bill_scatterplot.png",plot = flipper_bill_plot)
```

## Problem 2

```{r}

```

